Syntactic realization with data-driven neural tree grammars

### 2016-10-07 paper/draft.tex
paper changes

\begin{figure}
\centering
\begin{tabular}{|l|p{2cm}|p{2cm}|p{2.3cm}|p{2cm}|p{2.3cm}|}
\hline
Model & Embedding & Supertag & Root Category & Root Role & Leaf Category  \\ \hline
Fergus-N &  Convolution &  57.4\% & 81.8\% & 81.0\% & 86.8\% \\ \cline{2-6}
         &  Token       &  XX & XX & XX & \\ \cline{2-6}
\hline
Fergus-R &  Convolution &  36.4\% & 76.9\% & 78.3\% & 80.8\% \\ \cline{2-6}
         &  Token       &  XX & XX & XX & \\ \cline{2-6}
\hline
\end{tabular}
\label{table:accresults}
\caption{Classification accuracy by supertag and its individual properties}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{tabular}{|l|p{2cm}|c|c|}
\cline{3-4}
\multicolumn{2}{}{}& \multicolumn{2}{ |c| }{ \textbf{Accuracy}} \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Before A*} & \textbf{After A*}  \\ \hline
Fergus-N &  Convolution &  58.17\% & 57.40\% \\ \cline{2-4}
         &  Token       &  60.69\% & 55.56\% \\ \cline{2-4}
\hline
Fergus-R &  Convolution &  67.62\% & 57.04\% \\ \cline{2-4}
         &  Token       &  82.65\% & 62.73\% \\ \cline{2-4}
\hline
\end{tabular}
\label{table:accresults}
\caption{Classification accuracy by supertag and its individual properties}
\end{figure}
